Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-10 acl.2016/acl2016.tex
oov penalty

However, the model's query keys are the source and target phrase of each translation rule. Rather than storing the lexicalized re-ordering model separately, we shall integrating it into the translation model, eliminating the need to query a separate file. The lexicalized reordering model retains its own weights in the log-linear framework. The total weighted score is expected to be identical to the Moses baseline apart from edge case training configurations, for example, where the lexicalized reordering model is trained on a different dataset than the translation model.

>>>>

However, the model's query keys are the source and target phrase of each translation rule. Rather than storing the lexicalized re-ordering model separately, we shall integrating it into the translation model, eliminating the need to query a separate file. However, the model remain the same under the log-linear framework, including having its own weights. %The search algorithm will produce identical results to the Moses baseline apart from edge case training configurations, for example, where the lexicalized reordering model is trained on a different dataset than the translation model.
